\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-30 trunk/intro.tex
updates

Autonomous platforms in the marine environment have had a substantial
and immediate impact for both civil and military
applications. Autonomous Underwater Vehicles (AUVs) in particular have
altered the way oceanographers are able to reach beyond the surface
and make observations which are not only at higher resolution but have
altered both the discipline and impacted the engineering methodologies
behind Sampling, Control and Robotics itself \comment{need higher
  level citation here}. Yet challenges remain, principally in making
such robotic devices more attune to the environment, to sample large
swaths at the Meso-scale ($> 50$ km\textsuperscript{2}) and doing so
systematically and adaptively. Further, over the last two decades
substantial improvements in hardware including propulsion, battery
technologies and hardware have not been kept abreast of in software
especially in algorithmic methods in Sampling and Control and in
systematic engineering and software engineering development.

@@

Persistent and early legitimate criticism of deliberation on the other
hand also well articulated by Brooks
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep}
was targeting the performance of in-situ deliberation. Terrestrial
robotic platforms were well-known to frequently stop and ``plan''. In
the marine robotics world, such a situation would simply not be
permissible given the need to make continuous observations without
stopping an under-articulated robotic platform such as an AUV. However
algorithmic and implementational advances by the AI community over the
years has produced a range of planners with demonstrated embedded
capabilities \comment{cite}. Our work has been influenced by and in
turn influenced a wide range of activities in the field of AI Planning
and Plan Execution with demonstrated real-world and highly visible
capabilities in the Space domain \cite{mus98, rajan00, ai-chang04,
  bresina05} for NASA. Lessons learned have been applied to the world
of marine robotics which we bring together in this chapter. Important
lessons that were derived from this rich legacy involved the following:

@@

\begin{figure}[t]
  \centering
  \vskip-5pt
  \includegraphics[scale=0.325]{figs/MBARI-AUV.jpg}
  \caption{\small The MBARI \emph{Dorado} AUV on its support vessel
    the R/V \emph{Zephyr}.}
  \label{fig:auv-fig}
  \vskip-0.3cm
\end{figure}

>>>>

Autonomous platforms in the marine environment have had a substantial
and immediate impact for both civil and military
applications. Autonomous Underwater Vehicles (AUVs) in particular have
altered the way oceanographers are able to reach beyond the surface
and make observations which are not only at higher resolution but have
altered both the discipline and impacted the engineering methodologies
behind Sampling, Control and Robotics itself
\cite{Brierley08032002,ryan05,Thomas06,Yoerger01012007,Incze2009,Rigby10}. Yet
challenges remain, principally in making such robotic devices more
attune to the environment, to sample large swaths at the Meso-scale
($> 50$ km\textsuperscript{2}) and doing so systematically and
adaptively. Further, over the last two decades substantial
improvements in hardware including propulsion, battery technologies
and hardware have not been kept abreast of in software especially in
algorithmic methods in Sampling and Control and in systematic
engineering and software engineering development.

@@

Persistent and early legitimate criticism of deliberation on the other
hand also well articulated by Brooks
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep}
was targeting the performance of in-situ deliberation. Terrestrial
robotic platforms were well-known to frequently stop and ``plan''. In
the marine robotics world, such a situation would simply not be
permissible given the need to make continuous observations without
stopping an under-articulated robotic platform such as an AUV. However
algorithmic and implementational advances by the AI community over the
years has produced a range of planners with demonstrated embedded
capabilities
\cite{simmons94,Haigh98,alami:1998p820,chien00,mus98,teichteil07}. Our
work has been influenced by and in turn influenced a wide range of
activities in the field of AI Planning and Plan Execution with
demonstrated real-world and highly visible capabilities in the Space
domain \cite{mus98,rajan00,aichang04,bresina05} for NASA. Lessons
learned have been applied to the world of marine robotics which we
bring together in this chapter. Important lessons that were derived
from this rich legacy involved the following:

@@

\begin{figure}[t]
  \centering
  \vskip-5pt
  \includegraphics[scale=0.1]{figs/MBARI-AUV.jpg}
  \caption{\small The MBARI \emph{Dorado} AUV on its support vessel
    the R/V \emph{Zephyr}.}
  \label{fig:auv-fig}
  \vskip-0.3cm
\end{figure}

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section
\ref{sec:concepts}. \comment{add others} We conclude with Section
\ref{sec:conclusion}.
